---
title: "Indiana COVID-19 Project Data Dictionary"
author: "Eric Book"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
      html_document:
            toc: TRUE
            toc_float: TRUE
---


```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      out.width = "100%",
                      collapse = TRUE)

library(readr)
library(glue)
library(dplyr)
library(gt)
library(gtsummary)
```

Data files described in this dictionary are located in the [data](https://github.com/ercbk/Indiana-COVID-19-Tracker/tree/master/data) directory of the Indiana-COVID-19-Tracker repository and the [data](https://github.com/ercbk/Indiana-COVIDcast-Dashboard/tree/master/data) directory of the Indiana-COVIDcast-Dashboard repository.  
\
\

## Historical Weekly COVID-19 Cases by Age for Indiana

#### Description  
Processed data for Demographics [heatmaps](https://ercbk.github.io/Indiana-COVID-19-Website/demographics.html#cases-by-age) that shows a breakdown of weekly COVID-19 cases by age group.  

#### File name
age-cases-heat.rds  

#### Script  
Processing: [process-demog-data.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/process/process-demog-data.R)  

#### Raw Sources
Indiana Data Hub: [COVID-19 CASE DEMOGRAPHICS](https://hub.mph.in.gov/dataset/covid-19-case-demographics)  
tidycensus R package: [website](https://walker-data.com/tidycensus/), 2018 age populations for Indiana  

#### Notes  
Other variables:  
- `end_date`: Ordered factor; date of the last day of the weekly interval  
- `daily_cases`: Cases for the `end_date`; vestigial column that was used to calculate `weekly_cases`  
- `pop`: 2018 age populations for Indiana that's used to calculate `prop_cases`  
\

```{r, asis=TRUE}

ach <- read_rds("data/age-cases-heat.rds")
ach_var_defs <- c("Age group",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "Weekly count of COVID-19 confirmed cases by age group",
                  "Number of cases scaled to per 1000 residents per age group")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(ach,
            missing = "ifany",
            missing_text = "Missing",
            include = c(age_grp, weekly_cases, prop_cases)) %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = ach_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```
\
\
\

## Historical Weekly COVID-19 Deaths by Age Group for Indiana

#### Description  
Processed data for Demographics [line charts](https://ercbk.github.io/Indiana-COVID-19-Website/demographics.html#deaths-by-age) that shows counts and trends of weekly COVID-19 deaths by age group.  

#### File name
age-death-line.rds  

#### Script  
Processing: [process-demog-data.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/process/process-demog-data.R)  

#### Raw Sources
Indiana Data Hub: [COVID-19 CASE DEMOGRAPHICS](https://hub.mph.in.gov/dataset/covid-19-case-demographics)

#### Notes  
Other variables:  
- `end_date`: date of the last day of the weekly interval  
- `date_text`: date label for the chart  
- `tooltip`: pop-up text for points in chart with death counts and date  
\

```{r, asis=TRUE}

adl <- read_rds("data/age-death-line.rds")
adl_var_defs <- c("Age group",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "Weekly count of COVID-19 confirmed deaths by age group")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(adl,
            missing = "ifany",
            missing_text = "Missing",
            include = c(agegrp, weekly_total)) %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = adl_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```

\
\
\

## Historical Daily COVID-19 Hospital Admissions by Age Group for Indiana  

#### Description  
Raw data for the Hospitals [line charts](https://ercbk.github.io/Indiana-COVID-19-Website/hospitals.html#state-hospital-mortality-staffing-shortages-admissions) that shows daily COVID-19 hospital admissions by age group and gender.  

#### File name
age-hosp-line.rds  

#### Script  
Collection: [scrape-regenstrief-tableau.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/collection/scrape-regenstrief-tableau.R)  

#### Raw Sources
Regenstrief Institute: [dashboard](https://www.regenstrief.org/covid-dashboard/)

#### Notes  
This dataset is incomplete with random gaps between days.  

Other variables:  
- `date`: yyyy-mm-dd format  
\

```{r, asis=TRUE}

ahl <- read_rds("data/age-hosp-line.rds")
ahl_var_defs <- c("Age group",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "Daily COVID-19 male hospital admissions by age group",
                  "Daily COVID-19 female hospital admissions by age group",
                  "Daily COVID-19 total hospital admissions by age group")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(ahl,
            missing = "ifany",
            missing_text = "Missing") %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = ahl_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```
\
\
\

## Historical Daily ICU Beds and Ventilators for Indiana  

#### Description  
Raw data for the Static Charts [Hospitalizations, ICU Beds and Ventilator Availability](https://ercbk.github.io/Indiana-COVID-19-Website/static.html#Hospitalizations,_ICU_Beds_and_Ventilator_Availability) that shows resource counts of ICU beds and ventilators.  

#### File name
beds-vents-complete.csv  

#### Script  
Collection: [build-datasets.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/collection/build-datasets.R)  

#### Raw Sources
Indiana Data Hub: [COVID-19 BEDS AND VENTS](https://hub.mph.in.gov/dataset/covid-19-beds-and-vents)

#### Notes  
The source publishs daily excel spreadsheets with total resource counts, and these spreadsheets are collected and joined daily to produce a dataset with historical values.  

Other variables:  
- `date`: yyyy-mm-dd format  
\

```{r, asis=TRUE}

bvc <- read_csv("data/beds-vents-complete.csv")
bvc_var_defs <- c("Total ICU beds",
                  "Total ICU beds occupied with COVID-19 patients",
                  "Total available ICU beds",
                  "Total ventilators",
                  "Total ventilators being used by COVID-19 patients",
                  "Total ventilators being used by non-COVID-19 patients",
                  "Total available ventilators")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(bvc,
            missing = "ifany",
            missing_text = "Missing") %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = bvc_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  cols_width(vars(stat_0) ~ "150px") %>% 
  as_raw_html()

```
\
\
\

## Historical State Hospital Staff Shortages, Hospital Mortality Rate, Hospital Admissions and Ages Skewness of Admissions for Indiana  

#### Description  
Processed data for Hospitals [line charts](https://ercbk.github.io/Indiana-COVID-19-Website/hospitals.html#state-hospital-mortality-staffing-shortages-admissions) that shows state hospital staff shortages, hospital mortality rate, hospital admissions, and age skewness of hospital admissions towards older patients.  

#### File name
hosp-msas-line.rds  

#### Script  
Process: [process-hospitals-data.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/process/process-hospitals-data.R)  

#### Raw Sources
Regenstrief Institute: [dashboard](https://www.regenstrief.org/covid-dashboard/)  
Department of Health and Human Services: [COVID-19 Reported Patient Impact and Hospital Capacity by State Timeseries](https://beta.healthdata.gov/Hospital/COVID-19-Reported-Patient-Impact-and-Hospital-Capa/g62h-syeh)  
Department of Health and Human Services: [COVID-19 Reported Patient Impact and Hospital Capacity by Facility](https://beta.healthdata.gov/Hospital/COVID-19-Reported-Patient-Impact-and-Hospital-Capa/anag-cw7u)  

#### Notes  
Other variables:  
- `date`: Ordered factor, Month Day format  
\

```{r, asis=TRUE}

msas <- read_rds("data/hosp-msas-line.rds")
msas_var_defs <- c("Percent of reporting hospitals that have reported staffing shortages for that day. That percentage is averaged over a rolling, seven day window",
                   "Ratio of deaths of hospitalized COVID-19 patients and unique COVID-19 hospital admissions. Each rate is calculated over a rolling, 14-day window",
                   "Daily total of unique individuals that have tested positive for COVID-19 and been admitted to a hospital on the that day. Those daily counts are averaged over a rolling, seven day window",
                   "Measurement of the age makeup of the COVID-19 hospital admissions data. It's calculated over a rolling, 14 day window")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(msas %>% select(-date),
            missing = "ifany",
            missing_text = "Missing") %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = msas_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  cols_width(vars(stat_0) ~ px(150)) %>% 
  as_raw_html()

```
\
\
\

## Local Hospital Capacity for Indiana  

#### Description  
Processed data for the Hospitals [Local Hospital Capacity table](https://ercbk.github.io/Indiana-COVID-19-Website/hospitals.html#local-hospital-capacity) that shows capacity measures and counts of COVID-19 patients for hospitals at the local level.  

#### File name
hosp-react-tab.rds  

#### Script  
Process: [process-hospitals-data.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/process/process-hospitals-data.R)  

#### Raw Sources
Department of Health and Human Services: [COVID-19 Reported Patient Impact and Hospital Capacity by State Timeseries](https://beta.healthdata.gov/Hospital/COVID-19-Reported-Patient-Impact-and-Hospital-Capa/g62h-syeh)  

#### Notes  
Other variables:  
- `end_date`: date, yyyy-mm-dd format, end date of week interval  
- `hospital_name`: char, Name of hospital  
- `address`: char, Street address of hospital  
- `city_zip`: char, City and zip code  
- `county_name`: char, Name of county  
- `avgCovIceuTenKList`: nested list, `end_date` and average daily number of ICU beds being used by confirmed and suspected COVID-19 patients over the weekly interval  
- `avgCovHospTenKList`: nested list, `end_date` and average daily number of hospital beds being used by confirmed and suspected COVID-19 patients over the weekly interval  
- `avgTotImpBedsList`: `end_date` and average daily number of staffed total beds available over the weekly interval  
\

```{r, asis=TRUE}

hrt <- read_rds("data/hosp-react-tab.rds")
hrt_var_defs <- c("Proportion of the seven-day average of occupied ICU beds to the seven-day average of available ICU beds.",
                  "",
                  "Proportion of the seven-day average of occupied hospital beds to the seven-day average of available hospital beds.",
                  "")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(hrt %>% select(sev_day_icu_perc_occup, sev_day_hosp_perc_occup),
            missing = "ifany",
            missing_text = "Missing") %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = hrt_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  cols_width(vars(stat_0) ~ px(150)) %>% 
  as_raw_html()

```
\
\
\

## Historical Daily Tests, Cases and Deaths by Age for Indiana  

#### Description  
Raw data for Demographics [line charts](https://ercbk.github.io/Indiana-COVID-19-Website/demographics.html) that shows daily case and death counts by age group.  

#### File name
ind-age-complete.csv  

#### Script  
Collection: [build-datasets.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/collection/build-datasets.R)  

#### Raw Sources
Indiana Data Hub: [COVID-19 CASE DEMOGRAPHICS](https://hub.mph.in.gov/dataset/covid-19-case-demographics)  

#### Notes  
The source publishs daily excel spreadsheets with total resource counts, and these spreadsheets are collected and joined daily to produce a dataset with historical values.  
Other variables:  
- `date`: date, yyyy-mm-dd format  
\

```{r, asis=TRUE}

iac <- read_csv("data/ind-age-complete.csv")
iac_var_defs <- c("Age Group",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "",
                  "Number of cases by age group",
                  "Number of deaths by age group",
                  "Number of tests by age group",
                  "Percent of daily cases",
                  "Percent of daily deaths",
                  "Percent of daily tests")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(iac %>% select(-date),
            missing = "ifany",
            missing_text = "Missing") %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = iac_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  cols_width(vars(stat_0) ~ px(190)) %>% 
  as_raw_html()

```
\
\
\

## Historical Daily Cases and Deaths by Race for Indiana  

#### Description  
Raw data that shows daily case and death counts by race.  

#### File name
ind-race-complete.csv  

#### Script  
Collection: [build-datasets.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/collection/build-datasets.R)  

#### Raw Sources
The Covid Tracking Project: [The COVID Racial Data Tracker](https://covidtracking.com/race)  

#### Notes  
The source publishs data every 3 or 4 days.  
Other variables:  
- `date`: date, yyyy-mm-dd format  

There is a latin_x column for cases and deaths, but it's over 90% missing and only a few distinct values. A few columns have some TRUE/FALSE entries. I didn't investigate the reason behind these odd data entries.  

There are also around 30 columns completely composed of missing values.  
\

```{r, asis=TRUE}

irc <- read_csv("data/ind-race-complete.csv") %>%
  select_if(~any(!is.na(.))) %>% 
  select_if(~is.numeric(.)) %>% 
  select(!matches("latin_x"))


# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(irc,
            missing = "ifany",
            missing_text = "Missing") %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0)) %>%
  as_raw_html()

```
\
\
\

## Historical Weekly Median Age of Cases, Weekly Tests and Deaths for Indiana  

#### Description  
Processed data for the Demographics [bubble chart](https://ercbk.github.io/Indiana-COVID-19-Website/demographics.html#median-age-of-cases-tests-deaths) that shows the number of tests, number of deaths, and median age of the cases per week.  

#### File name
median-age-bubble.rds  

#### Script  
Processing: [process-demog-data.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/process/process-demog-data.R)

#### Raw Sources
Indiana Data Hub: [COVID-19 CASE DATA](https://hub.mph.in.gov/dataset/covid-19-case-data)  

#### Notes  
Other variables:  
- `end_date`: ordered factor, Month Day format; end date of weekly interval  
\

```{r, asis=TRUE}

mab <- read_rds("data/median-age-bubble.rds")
mab_var_defs <- c("Median age of cases for that week",
                  "Number of tests for that week",
                  "Number of deaths for that week")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(mab %>% select(-end_date),
            missing = "ifany",
            missing_text = "Missing") %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = mab_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  cols_width(vars(stat_0) ~ px(200)) %>% 
  as_raw_html()

```
\
\
\


## Historical Daily Hospital Admissions and Deaths for Indiana  

#### Description  
Raw data for the Hospitals [line charts](https://ercbk.github.io/Indiana-COVID-19-Website/hospitals.html#state-hospital-mortality-staffing-shortages-admissions) that shows daily COVID-19 hospital admissions, hospital deaths, and hospital death rate.  

#### File name
mort-hosp-line.rds  

#### Script  
Collection: [scrape-regenstrief-tableau.R](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/R/collection/scrape-regenstrief-tableau.R)  

#### Raw Sources
Regenstrief Institute: [dashboard](https://www.regenstrief.org/covid-dashboard/)

#### Notes  
This dataset is incomplete with random gaps between days.  

Other variables:  
- `date`: yyyy-mm-dd format  
\

```{r, asis=TRUE}

mhl <- read_rds("data/mort-hosp-line.rds")
mhl_var_defs <- c("Number of individuals hospitalized for COVID-19 who died while in the hospital",
                  "Number of unique individuals who have been hospitalized and tested positive for COVID-19",
                  "Percent of individuals hospitalized for COVID-19 who died while in the hospital")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(mhl %>% select(-date),
            missing = "ifany",
            missing_text = "Missing") %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = mhl_var_defs) %>% 
  modify_header(defs = "Definition") %>% 
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  cols_width(vars(stat_0) ~ "180px") %>% 
  as_raw_html()

```
\
\
\

## Historical Weekly Positivity Rates and Daily Cases per 100,000 Indiana Residents     

#### Description  
Processed data for the [Indiana COVIDcast Dashboard](https://ercbk.github.io/Indiana-COVIDcast-Dashboard/#dashboard) that shows weekly positivity rate and daily cases per 100,000 residents per metropolitan statistical area.    

#### File name
msa-cases100-posrate-historic.csv  

#### Scripts  
Processing: [process-hist-regional-dat.R](https://github.com/ercbk/Indiana-COVIDcast-Dashboard/blob/master/R/process-hist-regional-dat.R)  

#### Raw Sources
covidcast R package: [website](https://cmu-delphi.github.io/covidcast/covidcastR/)  
Michigan Disease Surveillance System: [website](https://www.michigan.gov/coronavirus/0,9753,7-406-98163_98173---,00.html)  
Wisconsin Department of Health Services: [website](https://data.dhsgis.wi.gov/datasets/covid-19-historical-data-by-county/data?orderBy=DATE&orderByAsc=false)  
Illinois Department of Public Health: [website](http://www.dph.illinois.gov/countymetrics?county=Adams)  
Indiana Data Hub: [website](https://hub.mph.in.gov/dataset?q=COVID)

#### Notes  
The missing values for `pos_rate` are partly because this dataset has a row for every day and the positivity rate is calculated every week. The other missing values are for Cincinnati, Louisville, and Evansville. At the time this dashboard was created, those states with counties included in those areas didn't publicly release the necessary data to calcuate the positivity rates for those areas.

Other variables:  
- `date`: yyyy-mm-dd format; date for daily `cases_100k`  
- `geo_value`: FIPS codes for `msa`  
- `start_date`: Start date of the weekly interval for `pos_rate`  
- `data_date`: Date when data was last updated
\

```{r, asis=TRUE}

msa_hist <- read_csv("../Indiana-COVIDcast-Dashboard/data/msa-cases100-posrate-historic.csv")
msa_hist_var_defs <- purrr::reduce(list("Metropolitan Statistical Area",
                                        rep("", 15),
                                        "Daily cases per 100,000 residents per MSA",
                                        "",
                                        "Weekly positivity rate per MSA",
                                        ""), append)

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(msa_hist,
            missing = "ifany",
            missing_text = "Missing",
            include = c(date, msa, cases_100k, pos_rate)) %>% 
  modify_header(update = list(
    label ~ 'Variable')) %>% 
  modify_table_body(dplyr::mutate, defs = msa_hist_var_defs) %>%
  modify_header(defs = "Definition") %>%
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>% 
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```
\
\
\

## Historical Daily Values of Delphi Research Group's Combined Indicator for Indiana    

#### Description  
Processed data for the [Indiana COVIDcast Dashboard](https://ercbk.github.io/Indiana-COVIDcast-Dashboard/#dashboard) that shows historic daily values of Delphi Research Group's Combined Indicator for each methropolitan statistical area.    

#### File name
dash-ci-line.rds  

#### Scripts  
Processing: [process-dashboard-data.R](https://github.com/ercbk/Indiana-COVIDcast-Dashboard/blob/master/R/process-dashboard-data.R)  

#### Raw Sources
covidcast R package: [website](https://cmu-delphi.github.io/covidcast/covidcastR/)  

#### Notes  
Other variables:  
- `time_value`: yyyy-mm-dd format; Daily
\

```{r, asis=TRUE}

dcl <- read_rds("../Indiana-COVIDcast-Dashboard/data/dash-ci-line.rds") %>% 
  filter(name != "<<<<<<< HEAD" & name != "=======" & name != ">>>>>>> 113d96e638fcac35d736d138e77e8b5d47d9a407")


dcl_var_defs <- purrr::reduce(list("Metropolitan Statistical Area",
                                   rep("", 15),
                                   "Delphi Research Group's “Combined” indicator"), append)

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(dcl,
            missing = "ifany",
            missing_text = "Missing",
            include = c(name, value)) %>%
  modify_header(update = list(label ~ 'Variable')) %>%
  modify_table_body(dplyr::mutate, defs = dcl_var_defs) %>%
  modify_header(defs = "Definition") %>%
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>%
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```
\
\
\

## Historical Weekly COVID-19 Statistics and Counts for Illinois Counties    

#### Description  
Raw data for the [Indiana COVIDcast Dashboard](https://ercbk.github.io/Indiana-COVIDcast-Dashboard/#dashboard) that shows various weekly COVID-19 county statistics for Illinois    

#### File name
illinois-tests-complete.csv  

#### Scripts  
Collection: [build-regional-dat.R](https://github.com/ercbk/Indiana-COVIDcast-Dashboard/blob/master/R/build-regional-dat.R)  

#### Raw Sources
Illinois Department of Public Health: [website](http://www.dph.illinois.gov/countymetrics?county=Adams) 

#### Notes  
These data are published in weekly intervals into a HTML table then scraped and collected.  

Other variables:  
- `week`: int; week of the year  
- `start_date`: yyyy-mm-dd format; First day of the weekly interval  
- `end_date`: yyyy-mm-dd formate; Last day of the weekly interval  
- `County`: char; Illinois county name  
- `New Cases per 100,000`: string; format: "\<int\> cases" or "\<int\> per 100k" or "\<int\> per 100kwarning"  
- `Test Positivity %`: string; format: "\<float\>%\\r\\n New Tests: \<int\>"  
- `(%) CLI ED Visits, Adults`: string; format: "\<int\>%"  
- `ICU (%) Available`: string; format: "\<float\>%"
\

```{r, asis=TRUE}

ill <- read_csv("../Indiana-COVIDcast-Dashboard/data/states/illinois-tests-complete.csv")


ill_var_defs <- c("Number of COVID-19 deaths per week per county",
                  "")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(ill,
            missing = "ifany",
            missing_text = "Missing",
            include = c(`Number of Deaths`)) %>%
  modify_header(update = list(label ~ 'Variable')) %>%
  modify_table_body(dplyr::mutate, defs = ill_var_defs) %>%
  modify_header(defs = "Definition") %>%
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>%
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```
\
\
\

## Historical Daily COVID-19 Test Results for Indiana Counties    

#### Description  
Raw data for the [Indiana COVIDcast Dashboard](https://ercbk.github.io/Indiana-COVIDcast-Dashboard/#dashboard) that shows daily COVID-19 county test results for Indiana    

#### File name
ind-tests-complete.csv  

#### Scripts  
Collection: [build-regional-dat.R](https://github.com/ercbk/Indiana-COVIDcast-Dashboard/blob/master/R/build-regional-dat.R)  

#### Raw Sources
Indiana Data Hub: [COVID-19 COUNTY-WIDE TEST, CASE, AND DEATH TRENDS](https://hub.mph.in.gov/dataset/covid-19-county-wide-test-case-and-death-trends) 

#### Notes  
Other variables:  
- `date`: yyyy-mm-dd format; Daily  
- `county`: County name
\

```{r, asis=TRUE}

ind <- read_csv("../Indiana-COVIDcast-Dashboard/data/states/ind-tests-complete.csv")


ind_var_defs <- c("Number of COVID-19 cases per day per county",
                  "Number of COVID-19 tests per day per county")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(ind,
            missing = "ifany",
            missing_text = "Missing",
            include = c(positives, num_tests)) %>%
  modify_header(update = list(label ~ 'Variable')) %>%
  modify_table_body(dplyr::mutate, defs = ind_var_defs) %>%
  modify_header(defs = "Definition") %>%
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>%
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```
\
\
\

## Historical Daily COVID-19 Test Results for Michigan Counties    

#### Description  
Raw data for the [Indiana COVIDcast Dashboard](https://ercbk.github.io/Indiana-COVIDcast-Dashboard/#dashboard) that shows daily COVID-19 county test results for Michigan    

#### File name
mich-tests-complete.csv  

#### Scripts  
Collection: [build-regional-dat.R](https://github.com/ercbk/Indiana-COVIDcast-Dashboard/blob/master/R/build-regional-dat.R)  

#### Raw Sources
Michigan Department of Health and Human Services: [COVID-19 Tests by County](https://www.michigan.gov/coronavirus/0,9753,7-406-98163_98173---,00.html) 

#### Notes  
Other variables:  
- `date`: yyyy-mm-dd format; Daily  
- `county`: County name
\

```{r, asis=TRUE}

mich <- read_csv("../Indiana-COVIDcast-Dashboard/data/states/mich-tests-complete.csv")


mich_var_defs <- c("Number of COVID-19 positive tests per day per county",
                  "Number of COVID-19 negative tests per day per county",
                  "Total number of COVID-19 tests per day per county")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(mich,
            missing = "ifany",
            missing_text = "Missing",
            include = c(positive, negative, total)) %>%
  modify_header(update = list(label ~ 'Variable')) %>%
  modify_table_body(dplyr::mutate, defs = mich_var_defs) %>%
  modify_header(defs = "Definition") %>%
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>%
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```
\
\
\

## Historical Daily COVID-19 Test Results for Wisconsin Counties    

#### Description  
Raw data for the [Indiana COVIDcast Dashboard](https://ercbk.github.io/Indiana-COVIDcast-Dashboard/#dashboard) that shows daily COVID-19 county test results for Wisconsin    

#### File name
wisc-tests-complete.csv  

#### Scripts  
Collection: [build-regional-dat.R](https://github.com/ercbk/Indiana-COVIDcast-Dashboard/blob/master/R/build-regional-dat.R)  

#### Raw Sources
Wisconsin Department of Health Services: [COVID-19 Historical Data by County](https://data.dhsgis.wi.gov/datasets/covid-19-historical-data-by-county/data?orderBy=DATE&orderByAsc=false) 

#### Notes  
Other variables:  
- `date`: yyyy-mm-dd format; Daily  
- `county`: County name
\

```{r, asis=TRUE}

wisc <- read_csv("../Indiana-COVIDcast-Dashboard/data/states/wisc-tests-complete.csv")


wisc_var_defs <- c("Number of COVID-19 positive tests per day per county",
                  "Number of COVID-19 negative tests per day per county",
                   "")

# table width responsive to length of var_defs text, so may not appear full.width
# use show_header_names to get col names being used by tbl_summary
tbl_summary(wisc,
            missing = "ifany",
            missing_text = "Missing",
            include = c(positive, negative)) %>%
  modify_header(update = list(label ~ 'Variable')) %>%
  modify_table_body(dplyr::mutate, defs = wisc_var_defs) %>%
  modify_header(defs = "Definition") %>%
  # show_header_names()
  as_gt() %>%
  tab_options(table.align = "left") %>%
  cols_align("left", vars(stat_0, defs)) %>%
  as_raw_html()

```
\
\
\
