---
output: 
   github_document
params:
      ind_combo_date: !r Sys.Date()
      pos_policy_date: !r Sys.Date()-1
      goog_mob_date: !r Sys.Date()-4
      region_dea_date: !r Sys.Date()-1
      region_pos_date: !r Sys.Date()-1
      county_pos_date: !r Sys.Date()-1
      daily_re_date: !r Sys.Date()-1
      pos_rate_date: !r Sys.Date()-1
      soc_dist_date: !r Sys.Date()-3
      hosp_iv_date: !r Sys.Date()-3
      
---


```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

![Noon Update](https://github.com/ercbk/Indiana-COVID-19-Tracker/workflows/Noon%20Update/badge.svg)
![Evening Update](https://github.com/ercbk/Indiana-COVID-19-Tracker/workflows/Evening%20Update/badge.svg)

# Indiana COVID-19 Tracker
Charts updated between noon and 1pm ET and at 6:30 pm ET  
Changelog located in [NEWS.md](https://github.com/ercbk/Indiana-COVID-19-Tracker/blob/master/NEWS.md)  

Repository to track COVID-19 data statewide and by county. Most of the State and County data for positive tests and deaths are gathered from The New York Times COVID-19 [repository](https://github.com/nytimes/covid-19-data) and The Indiana Data [Hub](https://hub.mph.in.gov/dataset). State policy [data](https://docs.google.com/spreadsheets/d/1zu9qEWI8PsOI_i8nI_S29HDGHlIp2lfVMsGxpQ5tvAQ/edit#gid=0) comes from Julia Raifman, Kristen Nocka, et al at Boston University.  
  
Governor Holcomb has begun scaling back policies aimed at stopping the spread of COVID-19. Much of his plan seems to follow the White House [plan](https://www.whitehouse.gov/openingamerica/), and both are simliar to the [guidelines](https://www.aei.org/research-products/report/national-coronavirus-response-a-road-map-to-reopening/) published by the American Enterpise Institute (AEI) and Johns Hopkins. Neither Governor Holcomb's nor the White House's plan includes the snapback (i.e. reverting to a previous stage) triggering conditions listed in the AEI proposal. Along with tracking virus spread metrics, I'll also be tracking as many of these triggers as I can with the data that's available. 

```{r}
ind_line_path <- glue::glue("plots/ind-combo-line-{params$ind_combo_date}.png")
knitr::include_graphics(ind_line_path)
``` 

   * Each point is the total cases that have accumulated until that date. The lines show the exponential nature of the spread of the virus at the beginning of the epidemic and changes in trend as policy and behavior changes.  
   * *Doubling time* is the amount of time it would take for the current total to double. It assumes that the rate of change is constant. The doubling time shown here assumes that the total change from yesterday to today (i.e. single day *growth rate*) will remain constant in the future. As we'll see in another chart, it's not a valid assumption in this situation, but it's interesting as a hypothetical. 
  
```{r ,align="center"}
pos_policy_path <- glue::glue("plots/pos-policy-line-{params$pos_policy_date}.png")
knitr::include_graphics(pos_policy_path)
```
  
   * This chart shows the number of daily positive cases on the y-axis versus the cumulative total of positive cases on the x-axis, where both axes are on a logarithmic scale. When the transmission rate lessens, the trend will decline and become increasingly vertical.  
   * In the AEI reopening guidelines, one of the triggers for returning to stage one is five or more consecutive days where the value of daily cases has increased.  
   * Details on the various stages of re-opening can be found at [Back-on-Track Indiana](https://backontrack.in.gov/2348.htm).

```{r}
hosp_iv_path <- glue::glue("plots/hosp-icu-vent-{params$hosp_iv_date}.png")
knitr::include_graphics(hosp_iv_path)
```

   * Even though Governor Holcomb hasn't explicitly stated the conditions that would necessitate a reversal of course to a previous stage, he did mention some benchmarks when discussing his guiding principles in his re-opening [speech](https://backontrack.in.gov/2362.htm). By negating a few of these, we can infer what some of the snapback conditions might entail.
      * An increase in daily hospitalizations for 14 consecutive days.
      * The proportion of available ICU beds to total ICU beds being below 40% for 14 consecutive days.
      * The proportion of available ventilators to total ventilators being below 70% for 14 consecutive days.  

```{r}
pos_rate_path <- glue::glue("plots/pos-rate-line-{params$pos_rate_date}.png")
knitr::include_graphics(pos_rate_path)
```

   * The Positive Test Rate is the number of positive test results divided by the number of tests administered over a period of time.
   * According to the World Health Organization (WHO), the positive test rate can be a good indicator of whether a virus testing program is sufficient. It finds that successful programs have a positive test rate in the range of 3% to 12%.  
   * A Johns Hopkins [article](https://coronavirus.jhu.edu/testing/testing-positivity) calculates this rate for states over three day windows and uses the WHO benchmark to classify state programs as adequate or not.  
   * Indiana Data Hub tends to revise its counts as it continues to collect more data. When analyzing this chart, it would be prudent not to assess the last few rates too confidently as they are likely to change.  
   * The green, horizontal bar shows the WHO recommended range from 3% to 12%.  
   * U.S. average calculated using data from [The COVID Tracking Project](https://covidtracking.com/api).

```{r}
soc_dist_path <- glue::glue("plots/soc-dist-line-{params$soc_dist_date}.png")
knitr::include_graphics(soc_dist_path)
```

   * Apple made available some of the [data](https://www.apple.com/covid19/mobility) it collects from its Apple Maps app which is used in its Mobility Trends Reports.  
   * The dataset has walking, transit, and driving mobility indexes, which represent counts of direction requests it receives from that app.  
   * As the virus spread and states mitigated with social distancing and closures, you can see the driving index trend take a dive. Given this correlation, it might be useful as an indirect measure of the level of social distancing taking place in these cities.  
   * Weekends are shown as vertical bars, and for comparison, the horizontal dashed line represents Indianpolis's current driving index.

```{r}
goog_mob_path <- glue::glue("plots/goog-mob-line-{params$goog_mob_date}.png")
knitr::include_graphics(goog_mob_path)
```

   * Google like Apple has released some of the [data](https://www.google.com/covid19/mobility/) it collects from its Maps app that it uses to produce Community Mobility Reports and product recommendations.  
   * From the "About this Data" section in the Report:
      * These reports show how visits and length of
stay at different places change compared to
a baseline.
      * The baseline is the median value, for the
corresponding day of the week, during the 5-
week period Jan 3–Feb 6, 2020.  
   * Weekends are shown as vertical bars.  

```{r, align="center"}
region_dea_path <- glue::glue("plots/region-dea-line-{params$region_dea_date}.png")
knitr::include_graphics(region_dea_path)
```

```{r, align="center"}
region_pos_path <- glue::glue("plots/region-pos-line-{params$region_pos_date}.png")
knitr::include_graphics(region_pos_path)
```

   * The y-axis has been transformed to the logarithmic base-10 scale. Slopes and trends of straight(-ish) lines are easier to compare than exponential curves.  
   * 7-day averages *greater* than 14 day averages indicate an *increasing* trend of positive cases or deaths.  
   * 7-day averages *less* than 14 day averages indicate a *decreasing* trend in positive cases or deaths. 

```{r, align="center"}
county_pos_path <- glue::glue("plots/county-pos-bar-{params$county_pos_date}.png")
knitr::include_graphics(county_pos_path)
```

   * The top 20 counties according to estimated average percent change are shown. Counties at the top are experiencing the highest average growth rates in positive test results.
   * The average percent changes are estimated using county data in a log-linear model.  
  
```{r}
daily_re_path <- glue::glue("plots/daily-re-line-{params$daily_re_date}.png")
knitr::include_graphics(daily_re_path)
``` 

   * The instantaneous effective reproduction number, R~e~ is an estimate of the average number of people that an infected person is spreading the virus to for that time window.  
   * Estimates *slighly lower* than 1 indicate that the spread of the virus is decreasing. Estimates *slightly larger* than 1 indicate a slow spread of the virus. Estimates of *2 or greater* mean the virus is spreading rapidly.  
   * R~e~ is estimated over a 7-day window, and the shaded area shows the 95% credible interval.
   * Further details on this metric can be found at a research [site](https://cbdrh.github.io/ozcoviz/#national-level-r_t) set-up by South Western Sydney Clinical School and the Centre for Big Data Research in Health. 